---
title: "Category Paths Basic"
author: "S. Aguinaga"
date: "10/21/2014"
output: html_document
---

Project Files
-------------

Project Folder:

- HOME/CategoryPaths/

Scripts:

- CategoryPaths/scripts/
- ~/Scriptus/pyths/dsg1

Description
-----------

<h3>Data-sets</h3>
Source Nodes
- Location: ```dsg1:/data/zliu8/sssp/```

We start with 100 start nodes (Wikipedia page ids)
```
/data/zliu8/sssp$ ls -1 | wc -l
100

ls -1 | head
sssp_1018340.txt
sssp_10568.txt
sssp_10671.txt
sssp_11054.txt
sssp_11121.txt
```
For each of these starting nodes we get the following set of games

```
~/CategoryPaths/gamesDatafiles$ head 1018340_wpgame_games.dat
src_pg, game,                            end_pg
1018340,08f2f5bb32504c3d8b5ad3dbc6ae92d2,19011063
1018340,fa2b9a1da0b64682b97f6344c262c0b5,9147836
1018340,3279c75c8b0341bbac09c3b44d0f0856,49603

```
This gives gives a total of ```42877``` games.  Here is an example of a starting node:


Processing file:  ```sssp_9475228.txt```

<h4>Shortest Path Length For These Games</h4>
The shortest path (L) for games starting with each start_node in our set. For example, file ```sssp_9475228.txt``` has ```175``` games.

```{r,echo=FALSE}
library(ggplot2);library(reshape2)
setwd("~/CategoryPaths/")
sp_for_games <- read.csv('ssspGamesDatFiles/9475228_to_path_game_sp.csv',sep=",",header=FALSE)
# qplot(sp_for_games$V3,binwidth=0.5, alpha = .5) +xlab("Path Length (L)")+xlim(0,max(sp_for_games$V3)+1)
data = data.frame()
df<- data.frame(sp_for_games)
data<-rbind(data,df)
# histograms
all_dat <- melt(data)
# one set of games
p<-ggplot(all_dat, aes(x=value, fill=variable)) + geom_histogram(binwidth=0.5, alpha=0.5, position="identity") + ylab("count/L") +xlim(0,4)
p
```

Distance distribution for all games that start with 100 unique page_ids.
```{r,echo=FALSE}
pathsSpAll <- read.csv('ssspGamesDatFiles/path_game_sp_1.csv',sep=",",header=FALSE)
# qplot(sp_for_games$V3,binwidth=0.5, alpha = .5) +xlab("Path Length (L)")+xlim(0,max(sp_for_games$V3)+1)
data = data.frame()
df<- data.frame(pathsSpAll)
data<-rbind(data,df)
# histograms
all_dat <- melt(data)
# one set of games
p<-ggplot(all_dat, aes(x=value, fill=variable)) + geom_histogram(binwidth=0.5, alpha=0.5, position="identity") + ylab("count/L") +xlim(0,4)
p
```


